material and methods

### 2017-08-22 man/ms_1_material_methods.Rmd
update mat and methods

To characterize the vegetation greeness of *Quercus pyrenaica* we used the Enhanced Vegetation Index (EVI) derived from MOD13Q1 product obtained by the Moderate Resolution Imaging Spectroradiometer (MODIS) sensor [@Didan2015]. EVI product consits of 16-day maximun value composite images (23 per year) of the EVI value with a spatial resolution of 231 m x 231 m.

EVI junto con NDVI ha sido utilizado para cuantificar la productividad primaria ... No obstante we used EVI instead of NDVI because it is more sensitive to change in high-biomass areas; EVI reduces the influence of atmospheric conditions on vegetation index values, and EVI corrects for canopy background signals [@Huete2002, @Krapivin2015].

NDVI sirve para estimar la producción primaria neta. Existen diferentes estudio que han evaluado el efecto de la sequía sobre la producción primaria neta utilizando NDVI.

Data were obtained using a Google Earth Engine script (:red_circle: cite gists) for the 2000 - 2015 period. We selected the pixels covering the distribution of Quercus pyrenaica forests in Sierra Nevada (*n* = 928 pixels). The EVI data are geometrically and atmospherically corrected and include information about the quality ass.... 
:red_circle:

>>>>

To characterize the vegetation greeness of *Quercus pyrenaica* we used the Enhanced Vegetation Index (EVI) derived from MOD13Q1 product obtained by the Moderate Resolution Imaging Spectroradiometer (MODIS) sensor [@Didan2015]. EVI and NDVI (Normalized Difference Vegetation Index) are the most common greenness vegetation indices. We used EVI instead of NDVI (Normalized Difference Vegetation Index) because EVI is more sensitive to changes in high-biomass areas (a serious shortcoming of NDVI); EVI reduces the influence of atmospheric conditions on vegetation index values, and EVI corrects for canopy background signals [@Huete2002, @Krapivin2015, @Cabello2012].

EVI product consits of 16-day maximun value composite images (23 per year) of the EVI value with a spatial resolution of 231 m x 231 m. Data were obtained using a Google Earth Engine script (:red_circle: cite gists) for the 2000 - 2016 period. We selected the pixels covering the distribution of Quercus pyrenaica forests in Sierra Nevada (*n* = 928 pixels). The EVI data are geometrically and atmospherically corrected and include information about the quality ass.... 
:red_circle:

`$NOTA$`: NDVI sirve para estimar la producción primaria neta. Existen diferentes estudio que han evaluado el efecto de la sequía sobre la producción primaria neta utilizando NDVI.
